\documentclass{article}
\oddsidemargin 0in
\textwidth 6.5in
\headsep 0in
\textheight 8.5in
\pagenumbering{arabic}
%set to 0 for real test (default), set to 1 to print answers
\newcount\showans
\showans=1
\newcommand{\ans}[1]{ \ifnum\showans=1 {\bf ANSWER #1.} \fi }
\begin{document}
{ \Large
\begin{center}
CS 341, F2007 - Test 1 (100 pts), Form A
\end{center}
}

\vspace{.1in}

\noindent
{\Large\bf INSTRUCTIONS:} Answer the multiple choice questions on the
answer sheet.  {\em Choose the best answer.  Mark only one answer per
question.}  For the essay problems, please answer the questions on the
paper provided.  {\em Write on only one side of each sheet of paper.
If you do write on both sides of any sheet you turn in, you {\bf will}
lose points.}

\vspace{.1in}

\begin{enumerate}

\item (3 points) C++ was originally designed at
  \begin{enumerate}
  \item IBM.
  \item HP.
  \item Microsoft.
  \item Apple.
  \item None of the above.  \ans{e}
  \end{enumerate}

\item (3 points) We are studying C along with C++ 
  \begin{enumerate}
  \item to make things more confusing.
  \item because you can't program C++ without knowing C.
  \item because knowing C makes you understand C++ better. \ans{c}
  \item because C and C++ require different compilers.
  \item None of the above.
  \end{enumerate}

\item (3 points) The first function run in a C++ program is the function
  \begin{enumerate}
  \item main().  \ans{a}
  \item cpp\_main().
  \item win\_main().
  \item start().
  \item None of the above.
  \end{enumerate}

\item (3 points) Identifiers in C++ 
  \begin{enumerate}
  \item must always start with a letter.
  \item are case insensitive.
  \item have a maximum length.
  \item may start with the underscore character.  \ans{d}
  \item None of the above.
  \end{enumerate}

\item (3 points) One of the few restrictions on declaring variables is
  \begin{enumerate}
  \item it must be declared just after a \{.
  \item it must be declared before used.  \ans{b}
  \item it must have a type modifier in the declaration.
  \item that even global variables must be declared inside functions.
  \item None of the above.
  \end{enumerate}

\item (3 points) Assume that z is 3.  The result of running the
expression $m = z * (k = 4 + (y = 3 * z))$ is
  \begin{enumerate}
  \item m is 9, k is 4, and y is 3.
  \item m is 39, k is 4, and y is 3.
  \item m is 27, k is 13, and y is 9.
  \item m is 39, k is 13, and y is 9.  \ans{d}
  \item None of the above.
  \end{enumerate}

\item (3 points) Consider the code:
\begin{verbatim}
    n = 2;
    n += n+(++n);
\end{verbatim}
What is the value of n after the code?
  \begin{enumerate}
  \item Not defined, don't do it.  \ans{a}
  \item This code produces a compiler error.
  \item 7
  \item 9
  \item None of the above.
  \end{enumerate}

\item (3 points) Consider the logical expression `` e1 \&\& e2 ''.
  \begin{enumerate}
  \item e1 and e2 are always evaluated.
  \item e2 is evaluated only if e1 is false.
  \item e2 is evaluated only if e1 is true.  \ans{c}
  \item None of the above.
  \end{enumerate}

\item (3 points) In C++, enum types 
  \begin{enumerate}
  \item allow naming of integer values.  \ans{a}
  \item can not be used with other enum types.
  \item produce unique numbers for each enum identifier.
  \item can not be used with floats or doubles.
  \item None of the above.
  \end{enumerate}

\item (3 points) In C and C++, a for loop
  \begin{enumerate}
  \item requires a new variable declared in the loop.
  \item calculates the number of times to run the loop before starting it.
  \item must have all expressions present in the ``for (e1; e2; e3)'' part.
  \item is just special syntax for a while loop.  \ans{d}
  \item None of the above.
  \end{enumerate}

\newpage
\item (3 points) The prototype ``void getInput (double \& val);''
specifies that
  \begin{enumerate}
  \item getInput returns a double.
  \item val is a call by value parameter.
  \item val is a pointer to a double.
  \item val is an array.
  \item None of the above.  \ans{e}
  \end{enumerate}

\item (3 points) Functions declared to be inline in C++ are
  \begin{enumerate}
  \item useless.
  \item may not be inline.   \ans{b}
  \item increase the time requirements for the program.
  \item will do textual substution like preprocessor macros.
  \item None of the above.
  \end{enumerate}

\item (3 points) Array parameters are like
  \begin{enumerate}
  \item call by value parameters and the entire array gets copied.
  \item call by value pointer parameters and just copy a pointer.  \ans{b}
  \item call by reference parameters to simple variables.
  \item no other kind of parameter.
  \item None of the above.
  \end{enumerate}

\item (3 points) If A and B are identical arrays, then the statement
``A = B;'' copies the array B into the array A.
  \begin{enumerate}
  \item True
  \item False  \ans{b}
  \end{enumerate}

\item (3 points) In C and C++, pointers may point at
  \begin{enumerate} 
  \item almost anything including functions.  \ans{a}
  \item just dynamic memory.
  \item dynamic memory and local variables.
  \item dynamic memory and global variables.
  \item None of the above.
  \end{enumerate}

\item (3 points) For dynamic memory manipulation, C++ uses
  \begin{enumerate}
  \item the operators malloc and free.
  \item the library routines new and delete.
  \item the library routines new and free.
  \item the operators new and free.
  \item None of the above.  \ans{e}
  \end{enumerate}

\item (3 points) In C++, there is no way to have the compiler
guarantee that an array passed into a function is not modified.
  \begin{enumerate}
  \item True
  \item False  \ans{b}
  \end{enumerate}

\newpage
\item (3 points) Given the declaration ``int x;'', the type
of ``\&x'' is
  \begin{enumerate}
  \item void *.
  \item int.
  \item void.
  \item int *.  \ans{d}
  \item None of the above.
  \end{enumerate}

\item (3 points) Given the declaration ``int *dp'', the code
``*(dp+ix)=0;'' is the same as
  \begin{enumerate}
  \item *dp = 0;
  \item *dp+ix = 0;
  \item dp[ix] = 0;  \ans{c}
  \item *dp*ix = 0;
  \item None of the above.
  \end{enumerate}

\item (3 points) The code ``int * ip = new int[100];''
  \begin{enumerate}
  \item will produce a compile error.
  \item creates a new integer in dynamic memory and initializes it to 100.
  \item creates a new array with 100 integers. \ans{c}
  \item None of the above.
  \end{enumerate}

\item (3 points) What will be printed from the following code?
\begin{verbatim}
     int ary[10] = { 3, 6, 9, 12, 15 };
     int *pa = ary;
     cout << *pa+2 << *(pa+2) << pa[5] << endl;
\end{verbatim}
  \begin{enumerate}
  \item It will segment fault.
  \item 9915
  \item \ 8 5 0 
  \item 590  \ans{d}
  \item None of the above.
  \end{enumerate}

\item (3 points) The value of the expression ``(1, 2, 3, 4)'' is
  \begin{enumerate} 
  \item 1. 
  \item 2.
  \item 3.
  \item 4.  \ans{d}
  \item None of the above.
  \end{enumerate}

\newpage
\item (3 points) The value of the expression
$( a<b ? (a>c ? a : c) : (b>c ? b : c) )$ is

  \begin{enumerate}
  \item not known from the above information.
  \item the minimum of a, b and c.
  \item the median of a, b and c. \ans{c}
  \item the maximum of a, b and c.
  \item None of the above. 
  \end{enumerate}

\item (3 points) The C++ code ``struct XYZ { int a; struct XYZ *b; } X;'' 
  \begin{enumerate}
  \item has a syntax error.
  \item declares X where X.b is of type XYZ*.  \ans{b}
  \item declares X where X.b is of type void *.
  \item None of the above.
  \end{enumerate}

\item (3 points) Given the code:
\begin{verbatim}
   struct mystruct {
       int size;
       int mydata[1000];
   };

   mystruct A, B, C;
\end{verbatim}
  \begin{enumerate}
  \item $A=B+C;$ is legal.
  \item $A=B=C;$ is legal.  \ans{b}
  \item $A==B==C;$ is legal.
  \item memcpy(A,B,sizeof(A)) is the only way to copy the structs.
  \item None of the above.
  \end{enumerate}


\item (6 points) Describe a very common bug in C and C++ using
the if statement.

\item (8 points) What are the 4 match rules for overloaded functions.
List them in order.

\item (6 points) A common loop looks like:
\begin{verbatim}
    int ix = 0;
    while (++ix < 10) { ... }
\end{verbatim}
What is the value of ix after the loop?  What would be the value if the
loop used ix++?

\item (5 points)  Why should you return a value from main?

\end{enumerate}

% comment out next line for sending to testing center
\end{document}


\newpage
\center{Answer Page For \underline{\hspace{3in}}

\newpage
\center{Please Leave Blank}

\newpage
\center{Answer Page For \underline{\hspace{3in}}

\newpage
\center{Please Leave Blank}

\newpage
\center{Answer Page For \underline{\hspace{3in}}

\end{document}
